Exploring the evolution of stellar rotation using Galactic kinematics

### 2020-04-29 paper/ms63.tex
adding citations

The mass dependence of magnetic activity lifetimes has been demonstrated
previously \racomment{for M dwarfs} \citep[\eg][]{west2008, newton2017,
kiman2019} and, if the detectability of a rotation period is considered to be
a magnetic activity proxy, then our results provide further evidence for a
mass-dependent activity lifetime.

>>>>

The mass dependence of magnetic activity lifetimes has been demonstrated
previously \racomment{for M dwarfs} \citep[\eg][]{west2008, reiners2009,
west2009, newton2017, kiman2019} and, if the detectability of a rotation
period is considered to be a magnetic activity proxy, then our results provide
further evidence for a mass-dependent activity lifetime.
